\documentclass[12pt,a4paper]{article}
\begin{document}
\begin{titlepage}
    \begin{center}
\line(1,0){500}\\
\huge{\bfseries DATA COLLECTION DESIGN CONCEPT ON STUDENTS WEEKEND TIME\\}
\line(1,0){500}\\
[0.25in]
mugumya leonalds|14/U/9560/PS\\
\end{center}
\end{titlepage}

\section{Purpose of data collection}
\begin{itemize}
\item To find out various activities done by student over the week. To get actual data on various weekend activities students engage in.
\item Type of data collected
\item Unorganized data of various events and activities that transpired in students’ life during weekends.
\end{itemize}

\section{Activities found during the data collection}
\begin{itemize}
\item Go out
\item Visit friends
\item Go swimming
\item Go to church
\item Attend events
\item Go back home
\end{itemize}
\section{Problems faced}
\begin{itemize}
\item People were on a move and barely had time for the questionnaire
\item Too many questions asked posed a threat to the interviewee
\item Incompleteness of forms that led to the cancelling
\item People feared to take any form of media because of insecurity.
\end{itemize}
\section{The questionnaire layout}
\begin{itemize}
\item Introduction of the interviewer to the interviewee
\item Details of the interviewer
\item Purpose of research explained
\end{itemize}
\section{Student details (interviewee)}
\begin{itemize}
\item Course Name
\item Reg No.
\item Gender
\end{itemize}
\section{ Take students photo}
\section{As a muk student which activities do you do over the weekend?}
\section{Among the above activities which one do you prefer most and why?}
\section{Any recording of you performing the above activities?}
\section{Do you also go for prime times at the pool on Saturdays?}
\section{Does the weekend give you enough time to do all the activities you want?}
\section{Any comment about this research?}
\section{Geolocation}
Thank you very much for participating in this research.
\end{document}







